\section*{Definitions}

Definitions are more detailed explanations of what words in the statutes are supposed to mean. The purpose of this section is to avoid misunderstanding because of translations from Swedish (of other languages) association terminology. The definitions are not part of the statutes but accepted interpretations of words in the statutes. 

\subsection*{Bills}
The same as motions except the suggestion is from the board (“propositioner” in Swedish). Note that individual board members can send motions as well; bills are suggestions from the entire board.

\subsection*{Discharge of liability}
During the spring meeting the association always votes about this. Discharge of liability means that the board is no longer responsible for mistakes they made during the year. If it is denied by the annual meeting, the members of the association have one year to press charges against the board (“Frågan om ansvarsfrihet” in Swedish).

\subsection*{General meeting}
The general meeting is the highest decision making organ of the association, the board functions on their behalf. 

\subsection*{Motions}
Suggestions from members that are decided about in the meeting (“motioner” in Swedish). 

\subsection*{Non-profit}
This is a translation of the Swedish word “ideell”.

\subsection*{Regulatory documents}
The regulatory documents are the statutes and the house rules.

\subsection*{Tellers}
Tellers have the role of counting votes during the general meeting.

\subsection*{Unanimous decision}
That no one objects the decision.

\subsection*{Unanimous vote}
If \emph{no-one} objects the suggestion being brought up.